---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# hw07-katiezinn

hw07-katiezinn created by GitHub Classroom

Welcome to my 7th homework assignment! For this assignment I added created a package that allows us to calculate the instantaneous growth of fish.

[![Build Status](https://travis-ci.org/katiezinn/FishGrowth.svg?branch=master)](https://travis-ci.org/katiezinn/FishGrowth)

# What did I do?
For this assignment I creating a package called **FishGrowth** with a useful function called `instantaneous_growth()`

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/katiezinn/FishGrowth)

__Note__: This R package is not mean to be "serious". It's just for learning purposes. 

# FishGrowth

This is an R package that allows you to calculate the instantaneous growth of a fish using this calculation:

Instantaneous growth = ( ( LN(final_length) - LN(initial_length) ) / # days between measurements ) *100

It is a useful function for comparing the growth rates of fish between experimental treatments.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("STAT545-UBC-students/hw07-katiezinn/FishGrowth")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
library(FishGrowth)
instantaneous_growth(15, 12, 5)
```

## For Developers

I developed this package for a class, if you have any serious inquiries (hahaha as if) feel free to contact me. 

